Title

### 2014-01-13 paper/parts/results.tex
Added some text to the paper.

\subsection{Comparing Different Flows Across Different Community-Types}

@@

>>>>

\subsection{Comparing Edges Across Different Community-Types}

We have defined communities using four different criteria: structure, activity, interaction, and content. For a given type of community, edges for a particular community may be partitioned into three sets: those from a node in the community to another node in the community (internal-to-internal), those from a node in the community to a node outside of the community (internal-to-external), and those from a node outside the community to a node inside the community (external-to-internal). See Figure~\ref{Fig-edge_types} for a schematic of this edge partitioning. For a meaningful community, we expect the distribution of weights within the community (internal-to-internal weights) to be different from the distribution of weights without the community (internal-to-external and external-to-internal).

@@

For example, Figure~\ref{Fig-edge_types} shows the distributions of hashtag-based weights for the largest community defined by mention-retweets. We see that the distribution of internal-to-internal hashtag weights has a longer tail, with edges

\begin{figure}[h!]
  \centering
\includegraphics[width=0.50\textwidth]{Figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}.}
\label{Fig-dist_across_community}
\end{figure}

\begin{table}
	\caption{The median value for the ratio of the median external/internal-to-internal/external weight to median internal-to-internal weight for the different community/weight pairings.}
	\centering
	\begin{tabular}{c | c | c  c  c  c}
		& & \multicolumn{4}{ c }{Community} \\ \hline
		\multirow{4}{*}{Weight} & & S & TE & MR & HT \\ \hline
		& TE & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
		& MR & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$\\
		& HT & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$ & $0.0 / 0.0$
	\end{tabular}
\end{table}
